Lens Modeling in \sw

### 2013-09-10 text/tex/results.tex
results

>>>>

Two additional sims were modeled by an expert, \asw{1hpf} and \asw{0vqg}.
Looking at the results for \gEr for those models in \figref{eR_per_sim}, we conclude that the performance of volunteers and experts is comparable.
Please note that the models of \asw{0vqg} with \gEr{, rel} around 0.25 (6935 -- 6937) are failed models that show the attempts of a single user, that came finally up with model 6938 as final result.
